\section{Threat Model}\label{sec:threat}

The full threat model is normative in
\texttt{Documentation/threat-model.md} of the source tree (commit
\texttt{9a63468}); this section summarizes the elements relevant to
v1 of the report.

\paragraph{Failure families.}
We distinguish two failure families to which the metadata trust
chain must respond:
\begin{description}
\item[Family A -- Poisson SEU.] Independent single-event upsets
  affecting isolated bits or bytes, distributed in space and time
  according to a homogeneous Poisson process. Typical of low-LET
  galactic cosmic ray background. Correctable by RS(255,239)
  shortened codes up to eight symbol errors per subblock.
\item[Family B -- correlated burst.] Spatially or temporally
  correlated corruption affecting contiguous bytes or repeated
  positions, typical of higher-LET particle tracks, single-event
  multiple-bit upsets, or early-stage device wear. May or may not
  be correctable depending on burst length and locality. The
  presence of Family B is detectable post-correction from the
  spatial distribution of corrected positions; format v4 will
  expose this via the Shannon entropy field
  (\cref{sec:future}).
\end{description}

\paragraph{Trust chain.}
At mount time and on every read of a metadata block, FTRFS verifies:
\begin{enumerate}
\item Magic number and version: strict equality with
  \texttt{FTRFS\_MAGIC} and \texttt{FTRFS\_VERSION\_CURRENT}.
\item CRC32 over the canonical serialization. If valid, accept.
\item If CRC fails, attempt RS decoding over the same logical
  region. If RS recovers a valid codeword, re-verify CRC; only on
  re-verification success is the block accepted, and a journal
  entry is written.
\item Range check on \texttt{s\_data\_protection\_scheme}: refuse
  values above \texttt{FTRFS\_DATA\_PROTECTION\_MAX}; the three
  high-order bytes of the field act as structural sentinels against
  single-byte high-side corruption.
\item Feature flag dispatch: unknown bits in
  \texttt{s\_feat\_incompat} cause mount refusal; unknown bits in
  \texttt{s\_feat\_ro\_compat} force read-only mount with a logged
  warning; unknown bits in \texttt{s\_feat\_compat} are logged
  informationally.
\end{enumerate}

The fail-closed posture (per axis~3.3) ensures that no metadata is
trusted unless every layer of the chain accepts it.

\paragraph{Out of scope.}
Active adversaries, side-channel attacks on the host CPU, and
pre-mount image tampering by an attacker with root access are out
of scope for v1. Stage~5 of the project plan addresses the
adversarial threat model; \cref{sec:future} describes the
planned syzkaller campaign and the security review activities
slated for v0.5.0.
